\RequirePackage{amsmath}
\documentclass[runningheads,a4paper]{llncs}
\pdfoutput=1

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{url}

\usepackage{soul}
\usepackage{amsmath}
\usepackage{complexity}
\usepackage[colorinlistoftodos]{todonotes}

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tabularx}
\usepackage{todonotes}


\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}

\newcommand{\qedproof}{\hfill $\square$ \medskip}
\renewenvironment{proof}{\par \noindent {\bf Proof}.}{\qedproof}

\newcommand{\PROBLEM}{CSCN problem}
\newcommand{\STEINER}{ST problem}

%\newcommand{\citep}[1]{\cite{#1}}
%\newcommand{\citet}[1]{\cite{#1}}
%\newcommand{\citen}{[\textit{citation needed}]}

\begin{document}

\mainmatter  % start of an individual contribution

\title{Extracting the Groupwise Core Structural Connectivity Network: Bridging Statistical and Graph-Theoretical Approaches}

% a short form should be given in case it is too long for the running head
\titlerunning{Extracting the Groupwise Core Structural Connectivity Network}
\author{\vspace{-2cm}}
\institute{\vspace{-1px}}

\author{Nahuel~Lascano\inst{1,2} 
    \and Guillermo~Gallardo\inst{1}
    \and Rachid~Deriche\inst{1}
    \and Dorian~Mazauric\inst{3}
    \and Demian~Wassermann\inst{1}}
\institute{Athena EPI, Universit\'e C\^ote d'Azur, Inria, France
\and
Computer Science Department, FCEyN, Universidad de Buenos Aires, Argentina
\and
ABS EPI, Universit\'e C\^ote d'Azur, Inria, France}
\authorrunning{N. Lascano et al.} 

\maketitle

\begin{abstract}
Finding the common structural brain connectivity network for a given population is an open problem, crucial for current neuroscience. Recent evidence suggests there's a tightly connected network shared between humans. Obtaining this network will, among many advantages, allow us to focus cognitive and clinical analyses on common connections, thus increasing their statistical power. In turn, knowledge about the common network will facilitate novel analyses to understand the structure-function relationship in the brain.

In this work, we present a new algorithm for computing the core structural connectivity network of a subject sample combining graph theory and statistics. Our algorithm works in accordance with novel evidence on brain topology. We analyze the problem theoretically and prove its complexity. Using 309 subjects, we show its advantages when used as a feature selection for connectivity analysis on populations, outperforming the current approaches.

\keywords{Group-wise connectome, core graph problem, brain connectivity, diffusion MRI}
\end{abstract}

\section{Introduction}
\input{introduction}

\section{Definitions, Problems and Contributions}\label{problem_section}
\input{definitions}

\section{Experiments and Results}
\input{experiments_results}

\section{Discussion and Conclusion}
\input{conclusion}


{\small \textbf{Acknowledgements} Authors acknowledge funding from ERC Advanced Grant agreement No 694665 : CoBCoM - Computational Brain 
Connectivity Mapping}

\vspace{-.5cm}
\bibliographystyle{splncs03}
\bibliography{library}
%\input{library.bbl}

\end{document}


