\section{Conclusion}
\label{sec:conclusion}

This paper presents a matrix factorization based approach to text
outlier analysis. The approach is designed to adjust well to the
widely varying structures in different localities of the data, and
therefore provides more robust methods than competing models. The
approach has the potential to be applied to other domains with
similar structure, and as a specific example, we provide experiments
on market  basket data. We also presented extensive experimental
results, which illustrate the superiority of the approach.  
Our code can be downloaded from 
\url{https://github.com/ramkikannan/outliernmf} and 
tried with any text dataset. 

In this paper, we had a parallel implementation using the
Matlab's parallel computing toolbox to run in multicore environments.
In the future, we would like to explore a scalable implementation
of our algorithm. The solution is embarrassingly parallelizable,
and would like to experiment in web scale data. One of the potential
extension is incorporating temporal and spatial aspects into the model.
Such an extension, make the solution applicable to emerging 
applications such as topic detection and streaming data. 
%In the recent times,
%approximate matrix factorization techniques are explored by
%randomly sampling the input matrix. We can reduce the computation
%time for very large matrices using such sampling techniques. We would like
%to explore a sampling based solution for our model. 
We experimented
the solution primarily on text data and market basket data. In future
work, we will extend this broader approach to other domains such as
video data.
