\section{Finiteness properties and first Betti numbers}
\label{secFinPropBetti}

We will now show how the results of Section \ref{secSESCoab} can be used to prove that under the assumption of strong enough finiteness properties the projections in Theorem \ref{thmNewCoab} have a finite index subgroup with even first Betti number.
 
\begin{proposition}
\label{propVB1}
 Let $G=\pi_1 X$ and let $\phi: G\rightarrow \G_{g_1}\times \dots \times \G_{g_r}$ be a homomorphism that is induced by a holomorphic map $f: X\rightarrow S_{g_1}\times \dots \times S_{g_r}$ with full image $\overline{G}=\mathrm{im}~ \phi$ of type $\mathcal{F}_m$ for $m\geq \frac{2r}{3}$. Then $\overline{G}$ is virtually coabelian of even rank and there is a finite index subgroup $\overline{G}_0\leq \overline{G}$ with even first Betti number.
\end{proposition}
\begin{proof}
It follows from Proposition \ref{propNewCoab} that $\overline{G}$ is virtually coabelian of even rank. Let $\G_{h_i}\leq \G_{g_i}$ be finite index subgroups, $1\leq i \leq r$ and $\phi: \G_{h_1}\times \dots \times \G_{h_r}\rightarrow \ZZ^{2N}=:Q$ be an epimorphism such that $\ker ~ \phi \leq \overline{G}$ is a finite index subgroup. 

By Lemma \ref{lemSurjComp}, the group $\phi\left(p_{i_1,\dots, i_{r-m}}(\overline{G})\right)  \leq Q$ is a finite index subgroup for all $1\leq i_1 < \dots < i_{r-m}\leq r$. Since $m\geq \frac{2r}{3}$, there is a partition of $\left\{1,\dots, r\right\}$ into three disjoint subsets $B_1=\left\{j_0=1,\dots, j_1\right\}$, $B_2=\left\{j_1+1,\dots, j_2\right\}$ and $B_3= \left\{j_2+1,\dots, j_3=r\right\}$ such that $|B_i|\geq r-m$. Thus, $A_i:= \phi\left(p_{B_i}(\overline{G})\right)\leq Q$ is a finite index subgroup. 

Define $P_i = \G_{h_{j_{i-1}}}\times \dots \times \G_{h_{j_i}}$. Consider the finite index subgroup $A=A_1\cap A_2 \cap A_3\leq \ZZ^{2l}$ and define finite index subgrups $P_{i,0}=\phi^{-1}(A)\cap P_i \leq P_i$. Consider the restriction $\overline{\phi}: P=P_{1,0}\times P_{2,0}\times P_{3,0}\rightarrow A$ of $\phi$ to the finite index subgroup $P\leq \G_{h_1}\times \dots \times \G_{h_r}$. 

Since $\phi(P_i)=A_i\geq A$, we have $\overline{\phi}(P_{i,0})=A$. Thus, the projection of $\overline{G}_0 = \ker \overline{\phi}$ onto the $P_{i,0}$ is surjective and we can therefore apply Proposition \ref{thmBettiZ}. Hence, the induced homomorphism $\left(\ker ~ \overline{\phi}\right)_{ab}= (\overline{G}_0)_{ab}\rightarrow P_{ab}$ is injective and
\[
 b_1(\overline{G}_0) = b_1(P)- 2N= b_1(P_{1,0})+b_1(P_{2,0})+b_1(P_{3,0})-2N
\]
However, $b_1(P_{i,0})$ is even, because $P_{i,0}$ is a finite index subgroup of the K\"ahler group $P_i$ for $i=1,2,3$. Thus, we obtain
\[
b_1(\overline{G}_0)\equiv 0 ~ \mathrm{ mod } ~ 2
\]
for the finite index subgroup $\overline{G}_0\leq \overline{G}$.
\end{proof}

\begin{corollary}
 With the notation of Theorem \ref{thmNewCoab}, assume that the group $\overline{G}$ has finiteness type $\mathcal{F}_m$. Then the projections onto $k\leq \frac{3m}{2}$ factors with indices $1\leq i_1 < \dots < i_k\leq s$ have a finite index subgroup with even first Betti number. 
 
 If, moreover, $G=\overline{G}$ and $s\leq \frac{3m}{2}$, then $r-s$ is even.
\end{corollary}
\begin{proof}
The first part is an immediate consequence of Proposition \ref{propVB1} and the fact that the homomorphism in Theorem \ref{thmNewCoab} is virtually induced by a holomorphic map.

For the second part, observe that after possibly passing to the finite index subgroup $G\cap \left(\G_{g_1}\times \dots \times \G_{g_s} \times \mathrm{Z}(G)\right)\leq G$, we may assume that $G$ is a direct product $G\cong G_0 \times \ZZ^{r-s}$ with $G_0\leq \G_{g_1}\times \dots \times \G_{g_s}$ full subdirect. Since $s\leq \frac{3m}{2}$, $G_0$ has a finite index subgroup $G_1\leq G_0$ with even first Betti number. The group $G_1 \times \ZZ^{r-s}$ is K\"ahler, so it also has even first Betti number. Therefore, $r-s$ is even.
\end{proof}


