We proposed an efficient ODC framework for kernel machines and validated the framework on structured regression machines on three human pose estimation datasets. The key idea is to equally  partition the data and create cohesive overlapping subdomains, where local kernel machines are computed for each of them. The framework is general and could be applied to various kernel machine beyond GPR, TGP, IWTGP validated in this work. Similar to TGP and IWTGP, our framework could be easily applied to the recently proposed Generalized  TGP~\cite{SMTGP_Elhoseiny15} which is based on Sharma Mittal divergence, a relative entropy measure brought from Physics community. We also theoretically justified  our framework's notion. 

\noindent \textbf{Acknowledgment.} This research was partially funded by NSF award \# 1409683.


\ignore{In this paper, we presented an ODC framework for structured regression kernel machines including GPR and TGP, applied to  3D pose estimation. The proposed model preserves accuracy while achieving a significant speedup in prediction, which is crucial for large scale prediction problems. The approach was evaluated on Poser, Human Eva and Human3.6M datasets. The key idea is to equally  partition the data and create cohesive overlapping subdomains, where local kernel machines are computed for each of them. The final prediction is then computed the predictions of the closest kernel machines. We should some interesting properties of the proposed framework including its applicability to a variety of the state-of the-art kernel methods.}