\section{Short exact sequences on abelianizations}
\label{secSESCoab}
Note that for a holomorphic map $f: X\rightarrow Y$, Lemma \ref{lemHodgeHol} does not provide us with the parity of the first Betti number $b_1(f_{\ast}\pi_1X)$ of the group $f_{\ast}\pi_1 X$, but only with the rank of the abelian subgroup $f_{\ast,ab}(\pi_1X)_{ab}\leq (\pi_1Y)_{ab}$. This is, because in general the map $f_{\ast,ab}:\pi_1 X_{ab} \rightarrow \pi_1 Y_{ab}$ is not injective. 

We will now show that in the case of coabelian subgroups of direct products of surface groups with strong enough finiteness properties we can actually obtain (virtual) injectivity and as a consequence we obtain that in fact $b_1(f_{\ast}\pi_1 X)$ is even. This will follow from more general group theoretic considerations.

We will make use of the following easy and well-known fact

\begin{lemma}
 Let $G$ and $H$ be groups and let $\phi: G\rightarrow H$ be an injective homomorphism. Then the following are equivalent:
 
 \begin{enumerate}
  \item the induced map $\phi_{ab}: G_{ab}\rightarrow H_{ab}$ on abelianisations is injective;
  \item $\phi(\left[G,G\right])=\phi(G)\cap \left[H,H\right]$.
 \end{enumerate}
 \label{lemInjonAbel}
\end{lemma}


It allows us to prove

\begin{proposition}
 Let $k\geq 1$, $r\geq 2$ be integers, let $G_1,\cdots, G_r$ be finitely generated groups and let $\psi : G=G_1\times \cdots \times G_r \rightarrow \ZZ^k$ be an epimorphism. Assume further that (at least) one of the following two conditions is satisfied:
 \begin{enumerate}
  \item $k=1$ and $\ker \psi$ is subdirect in $G_1\times \cdots \times G_r$;
  \item the restriction of $\psi$ to $G_i$ surjects onto $\ZZ^k$ for at least three different $i\in \left\{1,\cdots, r\right\}$.
 \end{enumerate}
 
 Then the map $\psi$ induces a short exact sequence 
 \begin{equation}
  1\rightarrow (\ker \psi)_{ab}\rightarrow (G_1\times \cdots \times G_r)_{ab}\rightarrow \ZZ^k\rightarrow 1
  \label{eqnSESab1}
 \end{equation}
 on abelianisations and in particular the following equality of first Betti numbers holds:
 \begin{equation}
  b_1(G)=k+ b_1(\ker \psi).
  \label{eqnBetti1}
 \end{equation}  
 \label{thmBettiZ}
\end{proposition}

\begin{proof}
 We will first give a proof under the assumption that Condition (2) is satisfied and will then explain how to modify our proof if Condition (1) is satisfied. Assume that Condition (2) holds and that (without loss of generality) the restriction of $\psi$ to each of the first three factors is surjective.
 
 It is clear that exactness of \eqref{eqnSESab1} implies the equality \eqref{eqnBetti1} of Betti numbers. Hence, we only need to prove that the sequence \eqref{eqnSESab1} is exact. Abelianisation is a right exact functor from the category of groups to the category of abelian groups. Hence, it suffices to prove that the inclusion $\iota : \ker \psi \rightarrow G$ induces an injection $\iota _{ab} : (\ker \psi)_{ab}\rightarrow G_{ab}$ of abelian groups.
 
 Since the image of $\psi$ is abelian, it follows that $\left[G,G\right]\leq \ker \psi$. We want to show that $\left[G,G\right]\leq \left[\ker\psi,\ker\psi\right]$. Since $\left[G,G\right]=\left[G_1,G_1\right]\times \cdots \times \left[G_r,G_r\right]$ it suffices to show that $\left[G_i,G_i\right]\leq \left[\ker\psi,\ker\psi\right]$ for $1\leq i \leq r$.
 
 We may assume that $i>2$, since for $i=1,2$ the same argument works after exchanging the roles of $G_i$ and $G_3$. Fix $x,y\in G_i$. Since the restrictions $\psi|_{G_j}:G_j\rightarrow \ZZ^k$ are surjective for $j=1,2$ we can choose elements $g_1\in G_1$ and $g_2 \in G_2$ with $\psi(g_1)=-\psi(x)$ and $\psi(g_2)=-\psi(y)$. 
 
 Then the elements $u:=g_1^{-1}\cdot x\in G$ and $v:=g_2^{-1}\cdot y\in G$ are in $\ker \psi$. Since $\left[G_i,G_j\right]=\left\{1\right\}$ for $i\neq j$ it follows that $\left[u,v\right]=\left[x,y\right]$. Thus, $\left[G_i,G_i\right]\leq \left[\ker\psi,\ker\psi\right]$ for $1\leq i \leq r$. Consequently $\left[G,G\right]\leq \left[\ker\psi,\ker\psi\right]$ and therefore by Lemma \ref{lemInjonAbel} the map $\iota_{ab}$ is injective.
 
 Now assume that Condition (1) holds. As before it suffices to prove that $\left[G_i,G_i\right]\leq \left[\ker \psi,\ker\psi\right]$ for $1\leq i \leq r$. To simplify notation assume that $i=1$. If we can prove that there is some element $\overline{g}_0\in G_2\times \cdots \times G_r$ such that for any $x\in G_1$ there is an integer $k\in \ZZ$ with $x\cdot \overline{g}_0^k \in \ker \psi$ then the same argument as before will show that $\left[G_1,G_1\right]\leq \left[\ker \psi,\ker\psi\right]$.
 
 Observe that we have the following equality of sets
 \[
  Q:=\left\{\psi(g_1,1)\mid (g_1,\overline{g})\in \ker \psi\leq G_1\times (G_2\times \cdots \times G_r)\right\} = \left\{\psi(1,\overline{g})\mid (g_1,\overline{g})\in \ker \psi \right\}\leq \ZZ.
 \]
  
 The set $Q$ is a subgroup of $\ZZ$, since it is the image of the group $\ker \psi$ under the homomorphism $\psi\circ \iota_1\circ \pi_1:G\rightarrow \ZZ$ where $\pi_1:G\rightarrow G_1$ is the canonical projection and $\iota_1: G_1 \rightarrow G$ is the canonical inclusion. Let $\overline{g}_0\in G_2\times \cdots \times G_r$ be an element such that $\psi(1,\overline{g}_0)=l_0$ generates $Q$.
 
 Since $\ker \psi$ is subdirect, for any $g_1, g_2 \in G_1$ there are elements $\overline{g}_1,\overline{g}_2 \in G_2 \times \cdots \times G_r$ such that $(g_1,\overline{g}_1),(g_2,\overline{g}_2)\in \ker\psi$ and therefore $\psi(g_1,1)=k_1\cdot l_0. \psi(g_2,1)=k_2\cdot l_0 \in Q$. It follows that $(g_1,(\overline{g}_0)^{-k_1}), (g_2,(\overline{g}_0)^{-k_2})\in \ker \psi$. Thus $\left[g_1,g_2\right] \in \left[\ker \psi,\ker \psi\right]$, completing the proof of the Theorem.
\end{proof}

As a direct consequence we obtain a constraint on K\"ahler groups

\begin{corollary}
 Let $r,k\geq 1$ be integers, let $G_1,\cdots, G_r$ be finitely generated groups and let $\psi :G_1\times \cdots \times G_r\rightarrow \ZZ^k$ be an epimorphism satisfying one of the Conditions (1) or (2) in Theorem \ref{thmBettiZ}. If $b_1(G_1)+\cdots + b_1(G_r) - k$ is odd then $\ker \psi$ is not K\"ahler.
 \label{corBettiZ}
\end{corollary}
\begin{proof}
 By Proposition \ref{thmBettiZ} the first Betti number of $\ker \psi$ is equal to $b_1(G_1)+\cdots + b_1(G_r) - k$ and therefore odd. Hence, $\ker \psi$ can not be K\"ahler.
\end{proof}

Corollary \ref{corBettiZ} provides us with an elementary proof of Corollary \ref{corNewCoabExs} in two special cases.
\begin{corollary}
 Let $\psi: \G_{g_1}\times \dots \times \G_{g_r}\rightarrow \ZZ$ be a non-trivial homomorphism. Then $\ker \psi$ has odd first Betti number and in particular is not K\"ahler.
\end{corollary}

\begin{corollary}
 Let $r\geq 3$ and let $\psi: \G_{g_1}\times \dots \times \G_{g_r}\rightarrow \ZZ^{2k+1}$ be a homomorphism such that $\psi|_{\G_{g_i}}$ is an epimorphism for $i=1,2,3$. Then $\ker \psi$ has odd first Betti number and in particular is not K\"ahler.
 \label{corOddb1}
\end{corollary}

As a consequence, we obtain:

\begin{corollary}
Let $H=\ker \psi_1 \times \ker \psi_2$ be the product of the kernels of two epimorphisms $\psi_1,\psi_2$ satisfying the conditions in \ref{corOddb1}. Then $H$ is a full subdirect product of surface groups, which is coabelian of even rank, has even first Betti number and is not K\"ahler.
\label{corExEvenB1}
\end{corollary}
\begin{proof}
 The group $H$ is not K\"ahler by Remark \ref{remNewCoabExs}. All other properties follow from Corollary \ref{corOddb1}.
\end{proof}

\begin{proof}[Proof of Corollary \ref{corExEvenB1Intro}]
This is an easy consequence of Corollary \ref{corExEvenB1}.
\end{proof}




